---
title: "QMM 5"
author: "Neetu"
date: "2024-11-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load necessary libraries
library(lpSolveAPI)
library(kableExtra)
```
```{r}
# Create a data frame to summarize factors and goals
df = data.frame(
  Factor = c("Total Profit", "Employment Level", "Next Year's Earnings"),
  "Product 1" = c(20, 6, 8),
  "Product 2" = c(15, 4, 7),
  "Product 3" = c(25, 5, 5),
  Goal = c("Maximize", "= 50", ">= 75")
)

# Display the data frame
df %>%
  kable(align = "c") %>%
  kable_classic() %>%
  add_header_above(header = c(" " = 1, "Product" = 3, " " = 1)) %>%
  add_header_above(header = c(" " = 1, "Unit Contribution" = 3, " " = 1)) %>%
  column_spec(1, border_right = TRUE) %>%
  column_spec(4, border_right = TRUE) %>%
  column_spec(5, border_right = TRUE)
```

##Question 1: Formulate Constraints
The production rates of the first, second, and third products are denoted as x1x_1x1, x2x_2x2, and x3x_3x3, respectively. The constraints can be expressed as follows:
•	Employment constraint: 6x1+4x2+5x3≤50
•	Earnings constraint: 8x1+7x2+5x3≥75 

We can write these constraints in deviation form:
•	For employment: y1=6x1+4x2+5x3−50 
•	For earnings: y2=75−(8x1+7x2+5x3) 

Where y1y is the positive deviation (excess employment) and y2y is the negative deviation (shortfall in earnings).


##Question 2: Define the Objective Function
The objective is to maximize total profit while maintaining workforce stability and ensuring minimum earnings. The objective function can be expressed as:
Maximize Z=20x1+15x2+25x3−5(y1++y1−)−2y2−

Subject to the constraints:
•	Employment: 6x1+4x2+5x3−y1++y1−=50 
•	Earnings: 8x1+7x2+5x3−y2++y2−=75 

Non-negativity of decision variables: x1,x2,x3,y1+,y1−,y2+,y2−≥0 


##Question 3: Implementing the LP Problem in R
```{r}
# Create the LP model
lprec = make.lp(2, 7)

# Set the objective function coefficients
set.objfn(lprec, c(20, 15, 25, -5, 5, 0, -2))
lp.control(lprec, sense = 'max')

# Add constraints
set.row(lprec, 1, c(6, 4, 5, 1, 0, 0, 0), indices = c(1, 2, 3, 4, 5, 6, 7))
set.row(lprec, 2, c(8, 7, 5, 0, 0, -1, 1), indices = c(1, 2, 3, 4, 5, 6, 7))

# Define right-hand side values
rhs = c(50, 75)
set.rhs(lprec, rhs)

# Set constraint types
set.constr.type(lprec, c("=", ">="))

# Solve the LP problem
solve(lprec)
```


#Results and findings
```{r}
# Retrieve the optimal objective value and decision variable values
optimal_value <- get.objective(lprec)
decision_vars <- get.variables(lprec)

cat("Optimal objective value:", optimal_value, "\n")
cat("Optimal production levels:\n")
cat("Product 1 (x1):", decision_vars[1], "\n")
cat("Product 2 (x2):", decision_vars[2], "\n")
cat("Product 3 (x3):", decision_vars[3], "\n")
cat("y1+ (Excess Employment):", decision_vars[4], "\n")
cat("y1- (Shortfall Employment):", decision_vars[5], "\n")
cat("y2+ (Excess Earnings):", decision_vars[6], "\n")
cat("y2- (Shortfall Earnings):", decision_vars[7], "\n")
```

##Conclusion
The LP problem was successfully formulated and solved using the specified constraints and objective function. The optimal objective value is 275, indicating the maximum profit achievable under the given constraints.

The optimal production levels are as follows:
•	Product 1 (x1): 0
•	Product 2 (x2): 0
•	Product 3 (x3): 15
•	Excess Employment (y1+): 5
•	Shortfall Employment (y1-): 0
•	Excess Earnings (y2+): 0
•	Shortfall Earnings (y2-): 0

These findings suggest that production should focus solely on Product 3 to achieve the maximum profit while maintaining the required employment and earnings levels. The positive deviation in employment indicates that there is some flexibility in workforce management without compromising profit.

