---
title: "QMM"
author: "Neetu"
date: "2024-09-07"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Back Savers Company
```{r}
## Define the data for Collegiate and Mini backpacks
data <- matrix(c(3, 45, 32, 2, 40, 24), ncol = 3, byrow = TRUE)
colnames(data) <- c("Material (sq ft)", "Labor (min)", "Profit ($)")
rownames(data) <- c("Collegiate", "Mini")
data_table <- as.table(data)
data_table

## Summary of the LP model
decision_vars <- c("x_C: Collegiate", "x_M: Mini")
objective_function <- "Maximize Z = 32x_C + 24x_M"
constraints <- c("3x_C + 2x_M <= 5000", "45x_C + 40x_M <= 84000", "x_C <= 1000", "x_M <= 1200", "x_C >= 0", "x_M >= 0")

# Print the summaries
decision_vars
objective_function
constraints
```
###Summary
a) Decision Variables: Let xC be the number of Collegiate backpacks produced, and xM be the number of Mini backpacks produced.

b) Objective Function: Maximize the profit: Z=32xC+24xM

c) Constraints:
•	Material Constraint:3x_C + 2x_M \leq 5000
•	Labor Constraint:Total labor available = 35 workers * 40 hours = 1400 hours = 84000 minutes
Therefore, the labor constraint should be:
45x_C + 40x_M \leq 84000
•	Sales Constraints:( x_C \leq 1000 ), ( x_M \leq 1200 )
 

d) Full Mathematical Formulation:
Maximize: Z=32xC+24xM
Subject to: ( 3x_C + 2x_M \leq 5000 )
            ( 45x_C + 40x_M \leq 84000 )
            ( x_C \leq 1000 )
            ( x_M \leq 1200 )
            
Non-negativity: x_C \geq 0, \quad x_M \geq 0

##Weigelt Corporation
```{r}
# Define the data for plants and product sizes
data_weigelt <- matrix(c(20, 15, 12, # Storage required per unit (sq ft)
                        13000, 12000, 5000, # Storage available at each plant (sq ft)
                        750, 900, 450), # Production capacity at each plant (units)
                        nrow = 4, byrow = TRUE)

# Assign row and column names
colnames(data_weigelt) <- c("Large", "Medium", "Small")
rownames(data_weigelt) <- c("Storage per Unit (sq ft)", "Plant 1 Capacity", "Plant 2 Capacity", "Plant 3 Capacity")

# Convert matrix to table format
data_table_weigelt <- as.table(data_weigelt)
data_table_weigelt
```


###Summary
a) Decision Variables: Let:
1. (X_{L1}, X_{M1}, X_{S1}): number of large, medium, and small units produced at Plant 1.
2. (X_{L2}, X_{M2}, X_{S2}): number of large, medium, and small units produced at Plant 2.
3. (X_{L3}, X_{M3}, X_{S3}): number of large, medium, and small units produced at Plant 3.

b) Linear Programming Model:
Maximize profit:
P = 420(X_{L1} + X_{L2} + X_{L3}) + 360(X_{M1} + X_{M2} + X_{M3}) + 300(X_{S1} + X_{S2} + X_{S3})

Constraints:
1. Capacity Constraints:
Plant 1: X_{L1} + X_{M1} + X_{S1} \leq 750
Plant 2:X_{L2} + X_{M2} + X_{S2} \leq 900
Plant 3: X_{L3} + X_{M3} + X_{S3} \leq 450

2. Storage Constraints:
Plant 1:20X_{L1} + 15X_{M1} + 12X_{S1} \leq 13000
Plant 2: 20X_{L2} + 15X_{M2} + 12X_{S2} \leq 12000
Plant 3: 20X_{L3} + 15X_{M3} + 12X_{S3} \leq 5000

3. Sales Constraints:
Total large units: X_{L1} + X_{L2} + X_{L3} \leq 900
Total medium units: X_{M1} + X_{M2} + X_{M3} \leq 1200
Total small units: X_{S1} + X_{S2} + X_{S3} \leq 750

4. Non-negativity Constraints:
X_{L1}, X_{M1}, X_{S1}, X_{L2}, X_{M2}, X_{S2}, X_{L3}, X_{M3}, X_{S3} \geq 0

